### 2023-09-14 main.tex
rew

@@

where $\Lambda_{\bm{m}}$ are the eigenvectors of $Q_{0}^{2L}$ corresponding to a configuration $\bm{m}$ of the chain. \\
Indeed, since the exchange relation \eqref{ExQ0B-charges} has an extra creation operator
that gives rise to a proliferation of terms that does not vanish, thus only part of the argument done in the $N=2$ case can be followed. However, as we will show in subsection \ref{subsection-NONSS-W}, a closed formula for the steady state can be written, since when acting on the vacuum the exchange relations do remain simple. 
Here $SYM$ is the following transformation. We introduce, the following indices $i_{j}$ with $j=1,\ldots,k_{1}+\ldots+k_{N}$, such that 

@@

where $Sym$ is the symmetric group. \\

@@

we finally have 

@@

Using \eqref{W-charges-Bad}, it is possible to find an explicit expression of the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N>2$ by actin with $W$ on the vacuum state 

@@

This steady state reads 

@@

\textbf{Remark}: relation \eqref{SteadyState-W-Good} holds only for the action of $W$ on the vacuum state $|\Psi_{0}^{0}\rangle$. Acting on different equilibrium eigenstates, exchange relations between $B_{i}^{2L-1}$ and $Q_{0}^{2L}$ are more difficult and we cannot rewrite \eqref{W-charges-Bad} in such a simple form. 

@@

To prove \eqref{SteadyState-W-Good} we do four steps. 

@@

We introduce the following notation:

@@

We first write some relations that will be useful in the proof:

@@

\textbf{Proof of \eqref{BActionVoid}: } using \eqref{B-charge} we have that 
\begin{align}
	B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=&2 \left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}\sum_{k=1}^{N}e_{kN}^{[a]}e_{jk}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber
	\\=&
	2\left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}e_{NN}^{[a]}e_{jN}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber\\=&
	\sum_{x=1}^{L}2L|N,\ldots,\tau_{x}=i,\ldots,N\rangle -2\sum_{x=1}^{L}(x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle
\end{align}
where we used the fact that 
\begin{equation}\label{eNN-action}
	 e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$
\begin{equation}\label{Dij-ref}
	D_{i,j}^{2L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial from the definition of \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ and for all $x\in\{1,\ldots,L\}$ 
\begin{equation}
	D_{i,j}^{2L}||N,\ldots,\tau_{x}=i,\ldots,N\rangle=-2|N,\ldots,\tau_{x}=j,\ldots,N\rangle
\end{equation}
The proof is trivial from \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ 
\begin{equation}\label{GoodRelation}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=-2B_{j}^{2L-1}|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{GoodRelation}:}
\begin{align}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle&= D_{j,i}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-2e_{ji}^{tot}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-4\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
	\\&=
	-2B_{j}|\Psi_{0}^{0}\rangle
\end{align}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i$
\begin{equation}\label{DijBk-different}
	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial following the one of \eqref{GoodRelation}. 
\item For all $ \forall i\in \{1,\ldots,N-1\}$
\begin{equation}\label{Dii-ref}
	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=|\Psi_{0}^{0}\rangle\qquad D_{N,N}^{2L}\Psi_{0}^{0}\rangle=(1+2L)|\Psi_{0}^{0}
\end{equation}
The proof is trivial using \eqref{Dii-charge} and \eqref{DNN-charge}. 
\item $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$
\begin{equation}\label{Diagonal-Q-void}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle=(2L+N)(1+L)|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{Diagonal-Q-void}:}
\begin{align}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\\&=
	\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle
	\\&=
	(N-NL-2L+2(N+1)L+2L^{2})|\Psi_{0}^{0}\rangle
\end{align}
where we used the fact that 
\begin{equation}
	\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\end{itemize}

@@

	&Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber\\&=B_{i}^{2L-1}\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})-2(D_{i,i}^{2L}+D_{N,N}^{2L}+2(D_{i,i}^{2L+1}-D_{N,N}^{2L+1}))\right)-2\sum_{\ell=0\;\ell\neq i}B_{\ell}^{2L-1}D_{\ell,i}\right\}\nonumber\\&

@@

Observe that \eqref{Two-Relation} also implies that 

@@

We have that, using \eqref{GoodRelation}, \eqref{Dij-ref} and \eqref{Dii-ref},

@@

Using \eqref{veryUsefulSeries} and observing that  we have that $2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)$ is diagonal we have that, for all $j\in{1,\ldots,k_{1}+\ldots+k_{N-1}}$ 

@@

\cite{Belliard2} 

@@

In Subsection \ref{subsection-exact} and \ref{SectionNonLocalTrasformation} we have found three similarity transformations, namely $S_{1}$, $S_{2}$ and $W$ between operators $H$, $H^{'},H^{''}$ and $H_{0}$. Using them simultaneously one can map the non-equilibrium Hamiltonian $H$ onto the equilibrium one as

@@

As a consequence we have that, for a fixed configuration $\bm{m}$, the non-equilibrium eigenvectors can be mapped to the equilibrium ones as

@@

\appendix
\section{Oscillator realization}\label{appA}

 The basis element $ (E_{ab})_{a,b\in\{1,\ldots,N\}}$ of $gl(N)$ can also be thought as proper compositions of the rising, and lowering operators of th Heisenberg Lie algebra
  \begin{equation}\label{creationOperators}
	\begin{cases}
	\oad_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = |n_{1},\ldots,n_{a}+1,\ldots,n_{N}\rangle\\
	\oa_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle =n_{a}|n_{1},\ldots,n_{a}-1,\ldots,n_{N}\rangle
	\end{cases}
\end{equation}
with commutaion relations
\begin{equation}
	[\oad_{a},\oa_{b}]=-\mathbbm{1}\,\delta_{ab}
\end{equation}
Therefore, we have that 
\begin{equation}
		E_{ab}=\oad_{a}\oa_{b}\qquad \forall a,b=1,\ldots N
\end{equation} 
fulfil the action on the basis vector \eqref{actionE} and the commutation relation \eqref{eq:comgl} 
\section{Exact steady state of $H$}\label{appB}

>>>>

\begin{equation}\label{Tau-Notation}

@@

where $\Lambda_{\bm{m}}$ are the eigenvectors of $Q_{0}^{2L}$ corresponding to a configuration $\bm{m}$ of the chain. Here $SYM$ is the following transformation. We introduce, the indices $i_{j}$ with $j=1,\ldots,k_{1}+\ldots+k_{N}$, such that 

@@

where $Sym$ is the symmetric group among $N-1$ objects. \\
In this case we do not have a closed formula as in the case of $gl(2)$. Indeed, the exchange relation \eqref{ExQ0B-charges} has an extra creation operator
This extra creation operator, mixes up the species different from $N$.  However, as we will show in subsection \ref{subsection-NONSS-W}, a closed formula for the non-equilibrium steady state can be written, since when acting on the vacuum the exchange relations do remain simple. 

@@

we finally obtain \eqref{W-charges-Bad}. 
%		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
%		|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

Using \eqref{W-charges-Bad}, it is possible to find an explicit expression of the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N>2$ by acting with $W$ on the vacuum state 

@@

@@

\textbf{Remark}: relation \eqref{SteadyState-W-Good} holds only for the action of $W$ on the vacuum state $|\Psi_{0}^{0}\rangle$. Acting on different equilibrium eigenstates, exchange relations between $B_{i}^{2L-1}$ and $Q_{0}^{2L}$ are more difficult because of the presence of creation operators that mixes up species and we cannot rewrite \eqref{W-charges-Bad} in such a simple form. 

@@

We prove \eqref{SteadyState-W-Good} in four steps. 

@@

We recall the following notation, already used in \eqref{Tau-Notation}:

@@

We first write and prove some relations that will be useful:

@@

\textbf{Proof of \eqref{BActionVoid}: } using \eqref{B-charge} we have that 
\begin{align}
	B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=&2 \left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}\sum_{k=1}^{N}e_{kN}^{[a]}e_{jk}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber
	\\=&
	2\left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}e_{NN}^{[a]}e_{jN}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber\\=&
	\sum_{x=1}^{L}2L|N,\ldots,\tau_{x}=i,\ldots,N\rangle -2\sum_{x=1}^{L}(x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle
\end{align}
where we used the fact that 
\begin{equation}\label{eNN-action}
	 e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$
\begin{equation}\label{Dij-ref}
	D_{i,j}^{2L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial from the definition of \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ and for all $x\in\{1,\ldots,L\}$ 
\begin{equation}
	D_{i,j}^{2L}|N,\ldots,\tau_{x}=i,\ldots,N\rangle=-2|N,\ldots,\tau_{x}=j,\ldots,N\rangle
\end{equation}
The proof is trivial from \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ 
\begin{equation}\label{GoodRelation}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=-2B_{j}^{2L-1}|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{GoodRelation}:}
\begin{align}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle&= D_{j,i}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-2e_{ji}^{tot}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-4\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
	\\&=
	-2B_{j}|\Psi_{0}^{0}\rangle
\end{align}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i$
\begin{equation}\label{DijBk-different}
	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial following the one of \eqref{GoodRelation}. 
\item For all $ \forall i\in \{1,\ldots,N-1\}$
\begin{equation}\label{Dii-ref}
	D_{i,i}^{2L}|\Psi_{0}^{0}\rangle=|\Psi_{0}^{0}\rangle\qquad D_{N,N}^{2L}|\Psi_{0}^{0}\rangle=(1+2L)|\Psi_{0}^{0}
\end{equation}
The proof is trivial using \eqref{Dii-charge} and \eqref{DNN-charge}. 
\item $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$
\begin{equation}\label{Diagonal-Q-void}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle=(2L+N)(1+L)|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{Diagonal-Q-void}:}
\begin{align}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\nonumber\\&=
	\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle\nonumber
	\\&=
	(N-NL-2L+2(N+1)L+2L^{2})|\Psi_{0}^{0}\rangle
\end{align}
where we used the fact that 
\begin{equation}
	\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\end{itemize}

@@

	&Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber\\&=B_{i}^{2L-1}\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})-2(D_{i,i}^{2L}+D_{N,N}^{2L}+2(D_{i,i}^{2L+1}-D_{N,N}^{2L+1}))\right)\right.\nonumber\\&\left.-2B_{i}^{2L-1}\sum_{\ell=1\;\ell\neq i}^{N-1}B_{\ell}^{2L-1}D_{\ell,i}^{2L}\right\}|\Psi_{0}^{0}\rangle

@@

Observe that \eqref{Two-Relation} also implies

@@

Moreover, using \eqref{GoodRelation}, \eqref{Dij-ref} and \eqref{Dii-ref},

@@

Using \eqref{veryUsefulSeries} and observing that  we have that $2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)$ is diagonal we have, for all $j\in{1,\ldots,k_{1}+\ldots+k_{N-1}}$ 

@@

\cite{belliard2} 

@@

In Subsection \ref{subsection-exact} and \ref{SectionNonLocalTrasformation} we have found three similarity transformations, namely $S_{1}$, $S_{2}$ and $W$ between operators $H$, $H^{'},H^{''}$ and $H_{0}$. Using them simultaneously one can map the non-equilibrium Hamiltonian $H$ onto the equilibrium one (i.e. $H_{0}$) as

@@

As a consequence for a fixed configuration $\bm{m}$, the non-equilibrium eigenvectors can be mapped to the equilibrium ones as

@@

\appendix
{\color{blue}
\section{Oscillator realization}\label{appA}

 The basis element $ (E_{ab})_{a,b\in\{1,\ldots,N\}}$ of $gl(N)$ can also be thought as proper compositions of the rising, and lowering operators of th Heisenberg Lie algebra
  \begin{equation}\label{creationOperators}
	\begin{cases}
	\oad_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = |n_{1},\ldots,n_{a}+1,\ldots,n_{N}\rangle\\
	\oa_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle =n_{a}|n_{1},\ldots,n_{a}-1,\ldots,n_{N}\rangle
	\end{cases}
\end{equation}
with commutaion relations
\begin{equation}
	[\oad_{a},\oa_{b}]=-\mathbbm{1}\,\delta_{ab}
\end{equation}
Therefore, we have that 
\begin{equation}
		E_{ab}=\oad_{a}\oa_{b}\qquad \forall a,b=1,\ldots N
\end{equation} 
fulfil the action on the basis vector \eqref{actionE} and the commutation relation \eqref{eq:comgl} }
\section{Exact steady state of $H$}\label{appB}
